Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-11 robdml.tex
tex

% contributions
In brief, our contributions include proposing:
%
\begin{enumerate}[nosep, noitemsep, leftmargin=*]
	%
	\item {\textit{Hardness Manipulation}} (HM) as a flexible and efficient
		tool to create adversarial example triplets for subsequent adversarial
		training of DML model.
		%
	\item \textit{Linear Gradual Adversary} (LGA) as a Graduate Adversary, \ie,
		a pseudo-hardness function for HM, which incorporates our empirical
		observations and can balance the training objectives during the
		training process.
		%
	\item \textit{Intra-Class Structure} (ICS) loss term to further improve
		model robustness (especially intra-class-wise), while such structure is
		neglected by existing methods. 
		%
\end{enumerate}

>>>>

% contributions
In brief, our contributions include proposing:
%
\begin{enumerate}[nosep, noitemsep, leftmargin=*]
	%
	\item {\textit{Hardness Manipulation}} (HM) as a flexible and efficient
		tool to create adversarial example triplets for subsequent adversarial
		training of DML model.
		%
	\item \textit{Linear Gradual Adversary} (LGA) as a Graduate Adversary, \ie,
		a pseudo-hardness function for HM, which incorporates our empirical
		observations and can balance the training objectives during the
		training process.
		%
	\item \textit{Intra-Class Structure} (ICS) loss term to further improve
		model robustness and adversarial training efficiency, while such structure is
		neglected by existing methods. 
		%
\end{enumerate}
